Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Raster added.
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@56 db7c848b-7755-4df2-b763-8796797afa52

>>>>

RASTeR~\cite{BGP:09} is an out-of-core and view-dependent real-time multiresolution
terrain rendering approach using a patch-based restricted quadtree triangulation.
For load-balanced parallel rendering~\cite{GMBP:10} it exploits fast hierarchical
view-frustum culling of the level-of-detail (LOD) quadtree for sort-first decomposition, and
uniform distribution of the visible LOD triangle patches for sort-last decomposition.
The latter is enabled by a fast traversal of the patch-based restricted quadtree
triangulation hierarchy which results in a list of selected LOD nodes,
constituting a view-dependent cut or \emph{front of activated nodes} through the LOD hierarchy.
Assigning and distributing equally sized segments of this active LOD front to the concurrent
rendering threads results in a near-optimal sort-last decomposition for each frame.
